### 2014-10-22 fundamentals/examples.tex
moves cyamore bit to the other cycamore bit

\section{Examples}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

@@

@@

\subsubsection{The Cyclus Additional Modules Repository}

\Cycamore, the \Cyclus additional modules repository, provides a fundamental 
set of agent archetypes for basic simulation functionality within \Cyclus.
Since the \Cyclus framework relies on external archetypes to represent the 
agents within a simulation, 
\Cycamore provides the basic archetypes a new user needs to get started running 
simple simulations. 
These archetypes support a minimal set of fuel cycle simulation goals and 
provide, by example, a guide to new developers who would seek to contribute 
their own archetypes outside of \Cycamore.

>>>>

\section{Demonstration}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

@@

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can be 
improved by

@@
